\clearpage

\thispagestyle{plain}
\pagenumbering{roman}
\setcounter{page}{6}
\quad \quad \quad  {\Large AN ABSTRACT OF THE THESIS OF}

\vspace{1.5cm}

\small{
\noindent {\underline{MOHAMAD ALI NOUREDDINE} \quad \quad for \quad \quad \quad \quad \quad \quad \quad \quad~{\underline{Master of Engineering}}

\noindent \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad ~{\underline{Major:} Electrical and Computer Engineering}
}

\vspace{1.5cm}

\noindent Title: \underline{Verification of Software and Embedded Systems using AIG Solvers}

\vspace{1.5cm}

It is critical for software and hardware developers to design 
correct and reliable systems. In particular, safety critical 
systems such as medical equipment, navigation control and 
targeting devices do not tolerate defects in their logical 
components. 
Static analysis techniques are used to check and prove correctness 
of logic components with respect to formal specifications. 
In particular, ABC is a model checker that takes an And-Inverter-Graph (AIG) circuit,
a directed acyclic graph with two input AND gates, inverters and 
memory elements, 
reduces it using synthesis algorithms, and checks it for correctness
using proof algorithms. 
%At a higher level, 
Existing techniques transform software programs
and embedded system design components into Conjunctive Normal Form (CNF)
formulae and Symbolic Model Verifier (SMV)
%\todo{what is SMV?} 
code, and use satisfiability (SAT) solvers and symbolic
model checkers, respectively, to check their validity 
within a user specified finite domain.
These techniques often fail to scale well with 
the increasing size of systems and with larger finite domains. 

In this work, we explore the use of AIG solvers to 
address the verification of software and embedded systems
subject to bounds on the data width of their variables.
\mytool{} translates imperative logic systems, written in a C-like language,
into AIG. 
\biptool{} translates an embedded system, written within the Behaviour-Interaction-Priority (BIP) framework,
into AIG. 
Both methods use the ABC AIG solver to reduce the generated AIG circuits using 
sequential synthesis algorithms, and then check them for validity. 
The solver either (1) proves the specifications valid within the finite domain, 
(2) generates a counter example and reports it to the developer for debugging,
or (3) reaches its computational bounds before making a decision. 
%\todo{Statements on how the system was evaluated and snapshot of the results. }
We evaluated \mytool{} against a set of array and list manipulation algorithms, 
and various benchmarks obtained from the second competition on software verification 
(SVComp'13). Results show that \mytool{} reaches bounds higher than those possible 
with the CBMC bounded model checker. It was also able to rank amongst the top three
tools in the software verification competition.
%
We also evaluated \biptool{} against two benchmarks, an Automatic Teller Machine (ATM) system 
and the Quorum consensus protocol. 
\biptool{} surpasses the NuSMV model checker on both designs. 


\clearpage
