\clearpage

\thispagestyle{plain}
\pagenumbering{roman}
\setcounter{page}{5}

\begin{center}
\LARGE{{\bf Acknowledgments}}
\end{center}

Foremost, I would like to thank God for giving me the chance to continue
my graduate studies at the American University of Beirut, and for allowing
me to enjoy the support of all the wonderful people I have met during this journey. 
It is also through the divine guidance of the Quoran and the Holy prophet Muhammad and
his family that I was able to keep faith throughout the hardships and obstacles 
that I have faced.

Imam Zainul Abideen (a.s.) says in his Treatise of Rights:
\begin{quotation}
{\em The right of the one who trains you through knowledge is magnifying him, respecting
his sessions, listening well to him, and attending to him with devotion. You should not raise
your voice toward him. You should never answer anyone who asks him about something, in order that he may be the one who answers. You should not speak to anyone in his session
nor speak ill of anyone with him. If anyone ever speaks ill of him in your presence, you
should defend him.}
%You should conceal his faults and make manifest his virtues. You should
%not sit with him in enmity or show hostility toward him in friendship. If you do all of this,
%God's angels will give witness for you that you went straight to him and learned his
%knowledge for God's sake, not for the sake of the people.
\end{quotation}
I am forever indebted to my thesis adviser, Fadi Zaraket, for the continuous guidance and help 
he provided me with during my period of graduate studies. His approach to logic and formal methods
is what attracted me towards this field and kept me interested in it. It is with 
his encouragement and accurate advice that I was able to tackle the problems I faced in my research. 
I would also like to extend my gratitude to Fadi for the confidence he put in me and for allowing me 
to extend the work he started in his PhD. 

I am also full of gratitude to my thesis committee members, Louay Bazzi and Wassim Masri, for their 
constructive comments and advice. I would also like to thank them for making my thesis an enjoyable
and  instructive experience. 

Furthermore, I could not have completed this stage of my academic life without the unconditional love,
constant care and support, and prayer of my beloved fianc\'{e} Samah Karim. Thank you for being by my side
and for listening to my constant nagging in the times where I faced obstacles in my research. I couldn't have 
imagined a better companion for me in my journey and my life. 

Finally, key to my academic success is the support
of my father, Ali, my mother, Sonia, 
and my brother, Houssein. I owe all of the goals I was able to reach in my life to their constant
care and encouragement. I would also like to thank them for the huge faith that they had in me 
all along the way, which has pushed me to reach my production limits and beyond. 
