%% Background chapter
In this chapter, we present formalisms used throughout this thesis. 
A reader well-formed in logic verification and sequential circuits may
wish to skip this section, using it only as a reference. 

Let $V=\set{v_1,v_2,\ldots,v_m}$ be a set of scalar 
variables and $A=\set{a_1,a_2,\ldots,a_n}$ be a set of 
array variables. 
\begin{definition}[terms] \label{def:term}
  \rm A {\em term} is either
  a variable $v\in V$,
 a constant $c\in \mathbb{Z}$, or 
 an indexed array variable of the form $a[t]$ 
 which denotes the $t^{th}$ element of $a$ where $a\in A$ and 
 $t$ is a term.
 Arithmetic expressions of the form 
 $-t, t_1+t_2, t_1-t_2, t_1*t_2, t_1/t_2, t_1\%t_2$ 
 are all terms where $t,t_1,t_2$ are terms and 
 $-,+,*,/,$ and $\%$ denote the substraction, 
 addition, multiplication, division and remainder operations,
 respectively. 
\end{definition}

\begin{definition}[Boolean term]
  \rm A constant from the set $\mathbb{B}=\set{\true, \false}$
  is a {\em Boolean term}. 
  The expressions 
  $t_1<t_2, t_1\le t2, t_1> t_2, t_1\ge t_2, t_1==t_2$ are
  all Boolean terms where $t_1,t_2$ are terms and $<,\le,>,\ge,$ and $==$ 
  denote smaller, less than or equal, bigger than, 
  bigger than or equal, and equal,
  respectively. 
  The expressions $b_1\&\& b_2, b_1 \|\| b_2, !b_1, ->, ==$ are 
  all Boolean terms where $b_1,b_2$ are Boolean terms and 
  $\&\&, \|\|, !, -> ,$ and $==$ denote logical conjunction, disjunction,
  negation, implication, and equivalence, respectively.
\end{definition}

\begin{definition}[First order logic formula]
  \rm A Boolean term is a {\em first order formula}. 
  A quantified formula of the form $Q q. b(q)$, where
  $Q\in \set {\forall, \exists}$ is either a universal
  or existential quantifier, $q$ is a 
  quantified variable, and $b(q)$ is a first order
  formula with $q$ as a free variable. 
\end{definition}

\section{Sequential circuits}
\label{s:back:crct_semantics}
The ABC solver operates on an sequential circuit 
representation of a program.

\begin{definition}[Sequential circuit]
\rm A {\em sequential circuit} is a tuple $\big( (V, E),G,
O\big)$.  The pair $(V,E)$ represents a directed graph on
vertices $V$ and edges $E \subseteq V\times V$ where $E$
is a totally ordered relation.  The function $G: V \mapsto
{\mathit types}$ maps vertices to ${\mathit types}$.
There are three disjoint types: {\em primary inputs}, {\em
bit-registers} (which we often simply refer to as {\em
registers}), and logical {\em gates}.  Registers have designated
{\em initial values}, as well as {\em next-state
functions}.  Gates describe logical functions such as
the conjunction or disjunction of other vertices. 
A subset $O$ of $V$ is specified as the {\em
primary outputs} of $V$.  
We will denote the set of primary input variables by $I$,
and the set of bit-register variables by $R$.  
\label{def:back:seq_circuit}
\end{definition}

\begin{definition}[Fanins]
\rm We define the direct {\em fanin}s of a gate $u$ to be
$\{v: (v,u)\in E\}$ the set of source vertices connected
to $u$ in $E$.  We call the {\em support} of $u$ $\{v:
(v\in I \vee v \in R) \wedge (v,u) \in \ast E\}$ all
source vertices in $R$ or $I$ that are connected to $u$
with $\ast E$, the transitive closure of $E$.
\label{def:back:fanins} 
\end{definition}

%The ABC solver restricts gates to have 2~fanins, and
%computes the NAND function; since NAND is functionally
%complete, this is not a limitation.  
%For the sequential
%circuit to be syntactically well-formed, vertices in $I$
%should have no fanins, vertices in $R$ should have
%2~fanins (the next-state function and the initial-value
%function of that register), gates should have two fanins,
%and every cycle in the sequential circuit should contain
%at least one vertex from $R$.  The initial-value functions
%of $R$ shall have no registers in their support.  
%All sequential circuits we consider will be well-formed. 

The ABC solver reasons about {\em And-Inverter-Graphs (AIG)}
which are acyclic sequential circuits with only AND gates and inverters.
All AND gates are restricted to have 2 fanins. 
Since AND gates and inverters are functionally complete, 
this is not a limitation. 
For the sequential
circuit to be syntactically well-formed, vertices in $I$
should have no fanins, vertices in $R$ should have
2~fanins (the next-state function and the initial-value
function of that register) and gates should have two fanins.
%and every cycle in the sequential circuit should contain
%at least one vertex from $R$.  
The initial-value functions
of $R$ shall have no registers in their support.  
All sequential circuits we consider will be well-formed. 

\begin{definition}[State]
\rm A {\em state} is a Boolean valuation to vertices in $R$. 
%A {\em concrete input} is a Boolean valuation to vertices 
%in $I$.
\end{definition}

\begin{definition}[Trace]
\rm A {\em trace} is a mapping $t: V \times \mathbb{N} \mapsto
\mathbb{B}$ that assigns a valuation to all vertices in
$V$ across time {\em steps} denoted as indexes from
$\mathbb{N}$.  The mapping must be consistent with $E$ and
$G$ as follows.  Term $u_{j}$ denotes the source vertex of
the $j$-th incoming edge to $v$, implying that
$(u_{j},v)\in E$.  The value of gate $v$ at time $i$ in
trace $t$ is denoted by $t(v,i)$.
\[
t(v,i)=
   \begin{cases}
      s^i_{v}            &:v \in I \ \text{with sampled value $s_{v}^i$}\\
      t(u_2, i-1)        &:v \in R,i>0,u_2:=\ \text{next-state of $v$}\\
      t(u_1, 0)       &:v \in R,i=0,u_1:=\ \text{initial-state of $v$}\\
      G_v\big(t(u_{1},i),...,t(u_{n},i)\big) &: v \ \text{is a combinational gate with function 
$G_v$}
   \end{cases} \newline
\]
\end{definition}

The semantics of a sequential circuit are defined with
respect to semantical traces.  Given an input valuation
sequence and an initial state, the resulting trace is a
sequence of Boolean valuations to all vertices in $V$
which is consistent with the Boolean functions at the
gates.  We will refer to the transition from one valuation
to the next as a {\em step}.  A node in the circuit is
justifiable if there is an input sequence which when
applied to an initial state will result in that node
taking value $\mbox{true}$.  A node in the circuit is
valid if its negation is not justifiable.  We will refer
to targets and invariants in the circuit; these are simply
vertices in the circuit whose justifiability and validity
is of interest respectively.

\section{The \thislanguage component language}
\label{s:back:etc}
\input{etcircuit}

%\section{Sequential circuits as C++ classes}
%\label{s:back:circuit_as_cpp}
%A sequential circuit can be seen as a C++ class with Boolean variables representing
%its registers, an initialization function, a next state function and an output
%function as shown in Figure~\ref{fig:seq_as_cpp}. 
%%
%The initialization function computes the set of initial values for all 
%the registers in the circuit. The next state function is responsible for computing 
%the next state functions and updating the values of all register variables in the 
%circuit. The output function finally returns the result of the computation of the 
%circuit given the values of the registers and the inputs.
%\cci{done} is an internal variable signaling that the circuit has 
%successfully executed. It is set by the \cci{nextStateComputation} function.
%
%\begin{figure}[bt]
%\begin{Verbatim}[fontsize=\relsize{-2.5}, numbersep=4pt,numbers=left]
%class SequentialCircuit {
%	bool registers [];
%	bool done;
%	
%	void intialiaze (bool inputs[]);
%	void nextStateComputation (bool inputs[]);
%	bool outputFunction (bool inputs[]);
%	
%	bool simulateCircuit (bool inputs[]) 
%	{
%		initialize(inputs);
%		while (!done) {
%			nextStateComputation (inputs);		
%		}
%		return outputFunction(inputs);
%	}	
%}
%\end{Verbatim}
%\caption{Sequential circuit as a C++ class}
%\label{fig:seq_as_cpp}
%\end{figure}


\section{ABC sequential solver}
\label{s:back:abc}
\input{abc}


