In this thesis, we presented two techniques with supporting tools, \mytool{} and \biptool{}, that target the verification of the imperative
programs and embedded systems.
\mytool~is a tool that takes 
an imperative program \Pm with a specification,
a precondition and postcondition pair \pair{\Pre}{\Post},
and checks
whether \Pm satisfies the specification. This check 
is performed  within a 
bound $b$ on the domain of the program and specification
variables (\prob);
i.e. when the bounded inputs of \Pm satisfy \Pre, 
the outputs of \Pm satisfy \Post. 
The tool translates the problem \prob~
into an equisatisfiable AIG.
\biptool{} is a tool that 
takes an input 
BIP design with a set of optional specifications, 
and translates it in an equisatisfiable AIG, having 
its own customized execution engine. 

Both tools pass the generated AIGs to the AIG synthesis
and verification tool ABC for
reduction and model checking. ABC employs several reduction 
algorithms that can be used to reduce the size of the 
AIG and thus the size of the decision problem. 
ABC also includes a set of different proof algorithms
that can be used to efficiently verify the AIGs generated
by \mytool{} and \biptool{}. 

As future work, we plan to extend \mytool{} with support 
for LTL specifications, specifically {\em System Verilog
Assertions} SVA. We will devise a synthesis algorithm
that generates AIGs from SVAs and use ABC to model check
designs annotated with SVAs. Furthermore, 
we plan to extend \biptool{} with more customization
to the execution engine, specifically by allowing the engine
to execute multiple interactions in parallel. We envision
that this parallelism will allow for the generation 
of more efficient AIGs, and thus improve the 
verification results.
