\mytool~targets the verification of imperative programs annotated with 
precondition and postcondition specifications. An imperative program 
is a sequence of instructions that describes in full details the 
steps that the execution unit must take to accurately 
implement the required functionality. In order to verify 
that a program accurately implements its functionality, the developer
provides a set of formal specifications in the form of 
a precondition-postcondition pair. A precondition is a FOL formula over the 
the program's inputs that specifies which combination of inputs are acceptable; 
i.e. under which inputs the program is expected to work. 
A postcondition is a FOL formula over the program's inputs 
and outputs that defines the program's expected output. The
postcondition relates the program's outputs to its inputs~\cite{bradley2007calculus}. 

Given a program \Pm, 
a precondition and postcondition pair \pair{\Pre}{\Post}, 
and a bound $b$ on the domain of \Pm~and its variables,
\mytool~checks whether \Pm satisfies its specifications 
($\Pm \models \pair{\Pre}{\Post}|_{b}$); i.e. when the bounded inputs 
of \Pm satisfy \Pre, the outputs of \Pm must necessarily satisfy \Post.
\mytool~accepts programs written an imperative language, \psqlanguage, 
a subset of C++ extended with support for FOL and a block synchronization 
construct, the \cci{do\_together} block.
The tool then translates the problem ($\Pm \models \pair{\Pre}{\Post}|_{b}$)
into an equisatisfiable AIG using a program counter encoding. 
The generated AIG has a single output $o$ that is set to $1$ iff 
\Pm violates its specifications. The tool then uses the ABC
sequential AIG model checker~\cite{brayton2010abc} to check that $o$ is never set to $1$. 
If the check is successful, \Pm satisfies its specifications. Otherwise, \mytool~
returns the violating trace (i.e. the counterexample) to the user for debugging 
of \Pm.

%% illustrative example 
%\section{Illustrative Example} \label{chap:c2aig:sec:illustrative}
\input{motivation}

%\section{Comparison with recent work}
\section{Limitations of translation to CNF}
\label{s:intro:limitations}
Existing tools such as CBMC~\cite{clarke2004tool}
check for pointer safety, within bound
array access and user defined assertions in C programs.
Given a C program and a bound on the range of variables, CBMC unwinds the program's 
loops and recursive functions, and unfolds the program 
into a Boolean (CNF) formula that asserts the specified properties. 
It then uses SAT methods and tools such as MiniSat~\cite{sorensson2005minisat}
to check the CNF formula for counter examples. 
%As the given bound increases, and the program becomes more complexe, the size
%of the generated CNF formula rapidly grows and SAT problem becomes practically
%impossible to solve. Moreover, programs containing unbounded loops might 
%even render the process of generating the CNF formula infeasible. 

\input{limitations}

\input{sebac}
%CBMC's check, if valid, is only as good as the bound for which 
%it made the check, any bug that occurs beyond this bound is not detected.

%% formalization
\section{The \psqlanguage~ imperative language} \label{chap:c2aig:sec:formalization}
The grammar in Figure~\ref{fig:grammar} describes \psqlanguage, \mytool's
imperative input language. It is composed of a subset of the C++
programming language, extended with first order logic support 
and some special constructs. A \cci{program} is a list of 
declarations and statements. Variables can be declared to be of two 
kinds: (1) {\em wires} and (2) {\em registers}. Wires are non-memory 
elements used to monitor the values of different variables or terms
in the program, at every instance in the program's execution. Once assigned
to a term, wires will reflect the value of the term at 
every point in the program. On the contrary, register variables 
are memory elements that only change value once they are the target
of an assignment statement executed at a specific program point. 
The value of a register variable is memorized between two different
assignment statements. In what follows, we refer by wires to 
wire variables, and by variables to register variables. 

A variable can either be single or an array. Arrays can be declared to 
have a constant predefined size, or can be left free to have the maximum
number of elements to be determined by \mytool's runtime engine.
Similarly, wires can either be singular or arrays. 
\mytool~currently support one dimensional and two dimensional arrays. 
Given a two dimensional array $a$ of size $n$ by $m$ where $n$ and $m$ are constants, 
the tool transforms $a$ into a single dimensional array $a'$ of size 
$n \times m$, and translates all array accesses $a[i][j]$ into accesses
of the form $a'[i \times (n \times m) + j]$. 


{\em Statements} can be assignment statements, control statements or 
synchronization statements. Assignment statements modify the state of
program by assigning new values to select program variables. Control 
statements are used to modify the control state of the program by 
selecting the next program location, possibly begin dictated by the 
value of a certain term. \mytool~supports the 
\cci{if-then-else} selection control statement and the \cci{while} loop
control statement. 
Synchronization statements start with the \cci{dotogether}  
modifier, and are used to enforce the execution of a list of data-independent
assignment or selection statements at the same program point
(equivalently, at the same clock cycle).


Additionally, \mytool~ provides support for {\em function definitions} and 
{\em function calls}. Defining and calling a function is done in the same manner 
as in a regular C++ program, with the exception that \cci{return}
statements must always be present at the end of a function's body.
\mytool~allows also allows the declaration of recursive functions.
Expressions in \psqlanguage~extend the definition of terms presented in 
Definition~\ref{def:term} of Chapter~\ref{chap:back} with the addition 
of allowing terms to also be function calls, as depicted by the notation
\cci{term\_with\_function\_call} on line 31 of Figure~\ref{fig:grammar}. 

%% FOL properties
\mytool~extends the subset of C++ above with support for FOL specifications,
written in the form of {\em pre-condition}, {\em post-condition}
pairs. FOL expressions are Boolean expressions that can be Boolean 
terms or function calls, or {\em quantified expressions}. A quantified expression 
is either universally (\cci{forall}) or existentially  (\cci{exists}) quantified.


\begin{figure}[h!]
\centering
\begin{Verbatim}[fontsize=\relsize{-1.0}, numbersep=4pt,numbers=left]
program: block+
block: (declaration | statement)
statement: assignment_statement | conditional_statement | 
                        loop_statement | sync_statement		

// declarations
declaration: variable_declaration | function_declaration | property_declaration
variable_declaration: modifier? type id (`[' num `]' (`[' num `]')?)?
                      (`=' term)?
function_declaration: type id `(' argument_list? `)'
                      `{' block* return_statement `}'

// statements
assignment_statement: target `=' expression `;'
sync_statement: `@dotogether' `{' (assignment_statement | conditional_statement)+ `}'
conditional_statement: `if' `(' expresssion `)' `{' block `}'
                       `else' `{' block+ `}'
loop_statement: `while' `(' expression `)' 
                `{' block+ `}'
return_statement: `return' expression `;'

// properties
property_declaration: precondition | postcondition
precondition: `@pre' id `{' property+ `}'
postcondition: `@post' id `{' property+ `}'
property: expression | quantified_property
quantified_property: (`forall'|`exists') `(' range `)'
                     `{' property+ `;' `}'   

// expressions
expression: term_with_function_call
function call: id `(' call_arguments? `)'
call_argument: id (`,' id)*

argument_list: variable_declaration (`,' variable_declaration)*
modifier: `wire' | `const'
specifier: `int' | `bool'            
target: id | target `[' expression `]'
range: id `[' expression `...' expression `]' 
\end{Verbatim}
\caption{The \psqlanguage~imperative language}
\label{fig:grammar}
\end{figure}

\section{Translation to AIG}
\label{chap:c2aig:sec:translation}
Given an imperative program \Pm written in the \psqlanguage~language, 
and annotated with a FOL precondition postcondition 
specification pair \pair{\Pre}{\Post}, 
\mytool{} transforms the tuple (\Pm, \pair{\Pre}{\Post}) into an 
\thislanguage~program \Pm'. The tool then synthesizes \Pm'
into an equisatisfiable AIG $C$ having a single output
representing the formula $\lnot \left( \Pre \land \Pm \implies \Post \right)$. 
The tool then uses the ABC AIG solver to verify the validity 
of $\lnot o$ and thus prove that \Pm satisfies its
specification pair \pair{\Pre}{\Post} if successful. If the validity check fails, 
the tool returns a counterexample to be used by the developer for debugging.

%% Step 1 : some code transformations
\subsection{Preprocessing} \label{chap:c2aig:subsec:preproc}
\mytool~first starts by transforming 
\Pm into an intermediate program \Pm' $= \rho ($\Pm$)$ where
$\rho$ is a code transformation function that simplifies function calls, 
recursive functions and properties. 
%In what follows, we assume that we are given an imperative
%program \Pm with a set of variables $V$.
%
\paragraph{Function calls.} 
$\rho$ does not inline functions; instead, it uses a program counter mechanism to
avoid inlining and reuse the same code and thus the same AIG after synthesis. 
Key to that is the transformation of function class as follows. 
%Details of this mechanism are presented in Section~\ref{chap:c2aig:sec:transformation_et}.
Let $f(args_f)$ by a call to function declaration $f_d(args_{f_d}$ where $args_f$ is a list 
of expressions passed as arguments to $f$, and $args_{f_d}$ is the list of 
arguments declared in $f_d$. Let $ret(f_d)$ be the return variable of $f_d$, 
and $args_f(i)$ and $args_{f_d}(i)$ be the i'th 
argument passed to $f$ and declared in $f_d$, respectively, for $0 \leq i \leq |args_f|$.

Consider the assignment statement $s = (target := f(args_f))$ where $target$ is the 
target of the assignment as defined in line 38 of Figure~\ref{fig:grammar}.
The transformation function $\rho(s)$ is defined as follows:
\begin{equation}
\rho(s) = 
\begin{cases}
 & \left(  ;_{i = 0}^{|args_f|} \left( args_{f_d}(i) := args_f(i) \right) \right) ; \\
 & call\_func(f_d) ~;~\left( target := ret(f_d) \right) 
\end{cases}
\end{equation}
The \cci{;} operator represents an ordering of the statements, where $s_1;s_2$
means that $s_1$ executes before (or possibly at the same time as) $s_2$. 
Intuitively, $\rho$ copies the arguments passed to the call $f$ onto
the arguments declared in the function declaration $f_d$. It then 
adds the \cci{call\_func($f_d$)} statement, a special statement
that redirects the control of the program to the starting point of $f_d$'s body. 
It finally assigns that $target$ of $s$ to the return variable of the function $f_d$. 


%Given a function declaration $f_{dec}$, 
%we denote by $args(f_{dec}) \subset V$ the list of arguments of $f_{dec}$,
%by $ret(f_{dec}) \in V$ the return variable of $f_{dec}$, and by $body(f_{dec})$ 
%the list of statements in the function $f_{dec}$. 
%Given a function call $f$, we denote by $f_{dec} = dec(f)$ the function 
%declaration corresponding to the call $f$, and by $args(f) \subset V$ 
%the list of arguments passed to $f$. Additionally, 
%we denote by $args(f)[i]$ and $args(f_{dec})[i]$ the i'th argument passed to $f$
%and declared in $f_{dec}$, respectively. 
%
%\noindent Given an assignment of the form $x := f_c$ where $x \in V$, 
%let $f_d = dec(f_c)$, $a_{f_c} = args(f_c)$ and $a_{f_d} = args(f_d)$,
%the transformation function $\rho(x := f)$ is defined as:
%\begin{equation}
%\rho(x := f_c) = \begin{cases}
%\left( \bigcirc_{i = 0}^{|a_{f_c}| - 1} a_{f_d}(i) := a_{f_c}(i) \right) \circ \\
%\rho(body(f_d)) \circ \left( x := ret(f_d) \right)
%\end{cases}
%\end{equation}
%%\set{args(dec(f))[i] := args(f)[i]~|~i \in 0\ldots|args(f)|} \\
%where $\circ$ is the concatenation operator. 
%\mytool~assigns all argument variables in $dec(f)$ to all variables passed
%in the argument list of $f$, it then executes the list of statements in the 
%body of the function, and replaces references to the function call $f$ 
%by references to the return variable of $dec(f)$. Figure~\ref{fig:trans:function_call}
%shows an example of applying the transformation function $\rho$ onto a program containing
%a function call \cci{foo(x,y)}. The statement \cci{body(foo)} on line 5 of $\rho ( $ \Pm $)$
%corresponds the actual execution of the body of the function \cci{foo}. 


\begin{figure}[bt]
\centering
\begin{tabular}{p{0.33\textwidth}|p{0.01in}p{0.33\textwidth}}
\begin{Verbatim}[fontsize=\relsize{-2.0}, numbersep=4pt,numbers=left,
frame=topline, framesep=4mm, label=\fbox{Program \Pm}]
int fact (int n) {
   int result;
   if (n == 0) {
      result = 1;
   } else {
      result = n * fact(n-1);
   } 
   return result;
}

y = fact (x);
\end{Verbatim}
& &
\begin{Verbatim} [fontsize=\relsize{-2.0}, numbersep=4pt,numbers=left,
frame=topline, framesep=4mm, label=\fbox{Program $\rho ( $ \Pm $)$}]
int fact::result [];
int fact (int [] n) {
    if (n[fact::sp] == 0) {
        result[fact::sp] = 1;    
    } else {
        n[fact::sp + 1] = n[fact::sp] - 1;
        fact::sp = fact::sp + 1;
        call_func(fact);
        fact::sp = fact::sp - 1;
        result[fact::sp] = n[fact::sp]
                   * fact::ret[fact::sp+1];    
    }
    return result[fact::sp];
}

fact::n[0] = x;
call_func(fact);
y = fact::ret[0];
\end{Verbatim}
\end{tabular}
\caption{Transformation function $\rho$ on function calls}
\label{fig:trans:function_call}
\end{figure}
%
\paragraph{Recursive functions.} 
Let $f_d (args_{f_d})$ be a recursive function with arguments $args_{f_d}$,
and let $f(args_f)$ be a {\em recursive call} to $f_d$, i.e. a call to $f_d$
from inside the body of $f_d$. Using $\rho$,
\mytool~emulates recursion by (1) adding a stack pointer variable
$sp_{f_d}$ that maintains the recursive depth of the current function call, 
and (2) increasing the dimensionality of all arguments and local variable of $f_d$
by 1. In other words, variables become arrays and arrays become two dimensional 
arrays. Subsequently, all assignments and references to arguments or local variables
of $f_d$ are replaced by array access terms indexed by the current value 
of $sp_{f_d}$.
The recursion depth (i.e. $sp_{f_d}$) is incremented before
each {\em recursive call} $f$ and decremented once it returns. 

Consider the assignment statement $s = (target := f(args_f))$ where $target$ is the 
target of the assignment as defined in line 38 of Figure~\ref{fig:grammar}, and 
$f$ is a recursive call to $f_d$.
The transformation function $\rho(s)$ is then defined as follows:
\begin{equation}
\rho(s) = 
\begin{cases}
  & \left(  ;_{i = 0}^{|args_f|} \left( args_{f_d}(i)[sp_{f_d}+1] := args_f(i) \right) \right) ; \\
 & \left( sp_{f_d} := sp_{f_d} + 1 \right) ; call\_func(f_d) ; \left( sp_{f_d} := sp_{f_d} - 1 \right) \\
 & \left( target := ret(f_d)[sp_{f_d}+1] \right) ; 
\end{cases}
\end{equation}
Note that arguments of $f_d$ to be assigned are indexed by the future 
value of the recursion stack depth pointer (i.e. $sp_{f_d}+1$) before the
the pointer is incremented. The same is applied to the return variable 
of $f_d$ after the pointer has been decremented. 

Additionally, consider the assignment statement $s = (target := f(args_f))$ where
$f$ is a non-recursive call to $f_d$, $sp_{f_d}$ is guaranteed to have a value 
of $0$ and the transformation function $\rho(s)$ is defined as:
\begin{equation}
\rho(s) = 
\begin{cases}
  & \left(  ;_{i = 0}^{|args_f|} \left( args_{f_d}(i)[0] := args_f(i) \right) \right) ; \\
 &call\_func(f_d) ; \left( target := ret(f_d)[0] \right) ; 
\end{cases}
\end{equation}

Figure~\ref{fig:trans:function_call}
shows an example of applying the transformation function $\rho$ onto a program containing
a recursive function call \cci{fact(n)} that computes the factorial 
of an integer \cci{n}.
The argument \cci{n} of \cci{fact} and the local variable \cci{result} are transformed into the
arrays \cci{fact::n} and \cci{fact::result}. \cci{fact::sp} is the recursive stack pointer
variable added by $\rho$ for the function \cci{fact}.
Local references to \cci{n} are \cci{result} are replaced 
by the sequence access terms \cci{fact::n[fact::sp]} and \cci{result[fact::sp]}.

Lines 6-11 of $\rho(\Pm)$ in Figure~\ref{fig:trans:function_call} show the 
result of applying $rho$ on the recursive function call \cci{fact(n-1)}
on line 6 of the program \Pm. The next value of the argument $n$ is assigned
to the current value of $n$ decremented by $1$, as shown in the statement
\cci{fact::n[fact::sp + 1] = fact::n[fact::sp] - 1}. The stack pointer variable
is then incremented before adding the function call statement \cci{call\_func(fact)}
that gives the control to the body of the function \cci{fact}. Once the function
call returns, the stack pointer variable is decremented, and any reference
to the return variable of \cci{fact} is replaced by an array access term to the 
next value of the stack pointer (\cci{fact::sp + 1}).
Lines 16-18 of \Pm' shows the result of applying $\rho$ to a non-recursive call
to \cci{fact}, in which the arguments and return variable of \cci{fact} are 
replaced by array access terms indexed by $0$.
%Given a recursive function declaration $f$,
%the transformation function $\rho$ increases the dimension of all 
%arguments and local variables of $f$ by $1$; i.e. variables are transformed 
%into arrays and arrays into matrices. All assignments and references to an 
%argument or a local variable are replaced by array or matrix access operators. 
%These new array accesses are indexed by a special added variable, the 
%{\em function stack pointer} \cci{sp}. This variable tracks the number of recursive
%calls to $f$, and is incremented before each call to $f$, and decremented once 
%the function call returns. 
%
%\noindent Given an assignment of the form $x := f_c$ where $x \in V$ and $f_c$
%is a call to a recursive function, 
%let $f_d = dec(f_c)$, $a_{f_c} = args(f_c)$, $a_{f_d} = args(f_d)$,
%and $sp_f$ be the function stack pointer of $f_d$,
%the transformation function $\rho(x := f)$ is defined as:
%\begin{equation}
%\rho(x := f_c) = \begin{cases}
%\left( sp_f = sp_f + 1 \right) \circ
%\left( \bigcirc_{i = 0}^{|a_{f_c}| - 1} a_{f_d}(i)[sp_f] := a_{f_c}(i)[sp_f] \right) \circ \\
%\rho(body(f_d)) \circ \left( x := ret(f_d)[sp_f]  \right) \circ \left( sp_f = sp_f - 1 \right)
%\end{cases}
%\end{equation}
%
\paragraph{Quantifiers.} 
Consider the assignment statement $s = \left(target := Q (i:[t_1 \ldots t_2]) \set{\mathcal{B}} \right)$
where $target$ is the target variable of the assignment, $Q$ is either `$forall$' or `$exists$',
$i$ is a quantified variable, $t_1$ and $t_2$ are terms representing the range of $i$, and 
$\mathcal{B}$ is a Boolean FOL formula. $\rho(s)$ is defined as follows:
\begin{equation}
\rho(s) = 
\begin{cases}
\left( Q_r := true \right) ; \left( i := t_1 \right) ; \\
while(i <= t_2) \{ \rho \left( Q_r := Q_r ~(\&\& ~or~ ||)~ \mathcal{B} \right) ; 
\left( i := i + 1 \right) \}
; \\ 
\left( target := Q_r \right)   
\end{cases}
\end{equation}
For the quantified expression $\left( Q (i:[t_1 \ldots t_2]) \set{\mathcal{B}} \right)$,
$\rho$ adds a Boolean return variable $Q_r$ that is initialized to $true$ and holds
the value of the expression. Then $\rho$ transforms the expression into a while loop
that iterates over all possible values of $i$, and assigns the return variable $Q_r$
to its current value conjuncted or disjuncted with the value of $\mathcal{B})$.
The type of the operation performed is determined by the nature of the quantifier; 
conjunction for the universal quantifier (`$forall$') and disjunction for the 
existensial quantifier (`$exists$'). $\rho$ finally adds the actual assignment 
statement of $target$ as $target := Q_r$. Note that $\rho$ is also applied 
to the update assignment to the variable $Q_r$ in order to handle the cases
where $\mathcal{B}$ is also quantified or it contains a function call. 


Figure~\ref{fig:trans:forall} shows an example of applying the transformation 
function $\rho$ on a program \Pm containing an assignment of the variable \cci{y}
to a universal quantifier. 
Note that we added the expression \cci{forall::ret} to the condition of the 
\cci{while} loop in order to allow for early exit of the loop. 
Additionally, in the case the bounds on the quantified variable are constants, 
we optimize the transformation by unrolling the loop into a single large
Boolean expression.

\begin{figure}[bt]
\centering
\begin{tabular}{p{0.33\textwidth}|p{0.01in}p{0.33\textwidth}}
\begin{Verbatim}[fontsize=\relsize{-2.5}, numbersep=4pt,numbers=left,
frame=topline, framesep=4mm, label=\fbox{Program \Pm}]
y = forall(int i:[0 .. N]) 
               { a[i] != e };
\end{Verbatim}
& &
\begin{Verbatim} [fontsize=\relsize{-2.5}, numbersep=4pt,numbers=left,
frame=topline, framesep=4mm, label=\fbox{Program $\rho ( $ \Pm $)$}]
forall::i = 0;
forall::ret = true;

while (forall::i <= N && forall::ret) {
    forall::ret = forall::ret 
                  && (a[i] != e);
    forall::i = forall::i + 1;
}

y = forall::ret;
\end{Verbatim}
\end{tabular}
\caption{Transformation function $\rho$ on universal quantifier}
\label{fig:trans:forall}
\end{figure}
%
\paragraph{Pre/Post conditions.} 
Consider the \psqlanguage~
precondition and postcondition declarations $@pre~ \Pre ~\{ \mathcal{B} \}$
and $@post ~\Post ~\{ \mathcal{F} \}$ where $\mathcal{B}$ and $\mathcal{F}$ are 
Boolean expressions. For brevity, we refer by $\Pre$ and $\Post$ to the precondition
and postcondition delcarations, respectively.  
The transformation function $\rho$ is defined as follows:
%\begin{equation}
\begin{eqnarray}
& \rho(\Pre) = \rho \left( x_\Pre := \mathcal{B} \right) \\
& \rho(\Post) = \rho \left( x_\Post := \mathcal{F} \right) ; assert(x_\Pre \implies x_\Post)
\end{eqnarray}
%\end{equation}
$\rho$ creates for each declaration a Boolean variable that is used to hold its value
across the program's execution. $\rho$ then replaces the precondition declaration \Pre~
by a statement that assign its created variable $x_\Pre$ to its declared FOL 
formula $\mathcal{B}$. Similarly, $\rho$ replaces the postcondition declaration 
\Post~by the statement $x_\Post := \mathcal{F}$. In order to resolve quantification
or function calls in $\mathcal{B}$ and $\mathcal{F}$, we also apply $\rho$ to the created
statements. 

Additionally, $\rho$ adds an assertion statement 
$assert(x_\Pre \implies x_\Post)$ after the postcondition assignment statement. 
This assertion statement will not 
be evaluated, instead it used the help \mytool~ determine the outputs to pass
to the ABC AIG solver for verification. 
%%
%%For each pre/post condition declaration, \mytool~
%%creates a Boolean variable that is assigned to the value of the FOL formula representing
%%the property. The property is evaluated and assigned to the declared variable at
%%the same location where the pre/post condition is declared. 
%%
%%Additionally, for the postcondition declaration, \mytool~ adds an assertion statement 
%%of the form $precondition \implies postcondition$. This assertion statement will not 
%%be evaluated, instead it used the help the synthesizer described in
%%Section~\ref{chap:c2aig:sec:transformation_et} determine the primary outputs to pass
%%to the ABC sequential solver for verification. 


All statements and expressions in \Pm~ that are not mentioned in 
this Section are kept unchanged by the transformation function $\rho$. 

\section{Tranformation to \thislanguage} \label{chap:c2aig:sec:transformation_et}
\input{CtoETCircuit}

\section{\thislanguage~to AIG}
\label{chap:c2aig:sec:etcirc_to_aig}
Given a bound $b$ on the bit width of variables,
\mytool~synthesizes an AIG by a direct translation of a \thislanguage~program \aigcircuit~into
a sequential circuit. The synthesis proceeds as follows.  
Scalar register variables and array elements are translated into vectors 
of $b$ bits registers, while Boolean variables and array elements are directly mapped
onto one bit registers. The \cci{init} block of \aigcircuit~is used to determine the 
initial value of the instantiated registers. 

The \cci{next} block of \aigcircuit~infers the next state functions for all 
registers in the AIG, including the program counter. For each variable, 
we translate the expression of its next state function into a hierarchy of 
multiplexers that reflect the ternary choice expressions in \aigcircuit's 
assignment expressions.

Finally, \mytool~builds the primary output of the AIG 
as the negation of the assertion statement introduced in the 
pre-processing step. Given a precondition \Pre~and 
a postcondition  \Post, the primary output $o$ will
be $\lnot (x_\Pre \implies x_\Post)$ where $x_\Pre$ and
$x_\Post$ are the precondition and postcondition variables
introduced in the pre-processing step. 