We evaluate \mytool{} against three different program verification benchmarks. 
We first present a case study of linear and binary search and compare 
\mytool's results with those obtained from CBMC.
The second
set of benchmarks 
contains standard functions such as searching, sorting, linked list operations
and array partitioning. 
The third set contains benchmarks
from the second competition on Software Verification
(SV-COMP 2013)~\cite{svcomp}, a competition aimed at the thorough evaluation of 
automatic program verification tools. We ran all experiments on an
Intel Core i7 machine with 8 GB memory. 

\section{Searching: \mytool{} and CBMC}
\label{chap:res:casestudies}
\input{cases}

\section{Standard benchmarks}
\label{chap:res:standardbench}
\input{results_table_stand}
Table~\ref{tb:psq:standard} shows the results of applying 
\mytool{} on a set of standard program functions. The first column shows
the program \Pm to verify. \cci{ls} stands for {\em linear search}, 
\cci{bs} stands for {\em binary search}, \cci{bsort} stands for 
{\em bubble sort}, \cci{ss} stands for {\em selection sort},
\cci{a-p} stands for {\em array partitioning}, \cci{lli} stands for 
{\em linked list insert} and \cci{llr} stands for {\em linked list remove}. 
The column $b$ shows the chosen bit width for the variables in \Pm. 
Table~\ref{tb:psq:properties:standard} lists the properties verified for each of the 
standard benchmarks. 

\input{tb_properties}

To evaluate the size of the generated AIGs, we report on the 
number of latches (\cci{lat}), the number of AND  gates (\cci{and})
and the number of logic levels (\cci{lev}) as recorded by the 
ABC tool. We show the size of the AIGs before and after applying 
synthesis and reduction algorithms. We use common synthesis 
algorithms such structural sweeping ({\em ssweep}), 
retiming ({\em retime}), refactoring ({\em refactore})
and several other combinations of algorithms provided by ABC. 

For performance evaluation, the column {\em Ver.} shows the 
time taken by the verification algorithm and the column {\em Total} 
shows the total time taken by ABC to perform both synthesis (reduction)
and verification. 
The set of provided programs are all correct (\ie
contain no bugs), the {\em Check} column shows the result of the 
proof algorithm applied by ABC. A conclusive check ($\checkmark$) 
indicates that the solver was able to assert that the program
satisfies its specifications. A non conclusive check (N/A) 
indicates that the solver hit the time limit before returning 
a validity answer. We set a time-out of $1800$ seconds on induction based
proof algorithm and a $1000000$ {\em Binary Decision Diagrams} 
(BDD) size limit for algorithms based on 
BDD reachability. The amount of memory that \mytool{} 
is allowed to use is only limited by the machine's physical limit, \ie $8$ GB.

The results in Table~\ref{tb:psq:standard} clearly show the advantage that
using the sequential circuit encoding provides. The ABC synthesis engine is always
able to rewrite the generated AIG in a way to greatly reduce the number of AND gates
and logic levels. For example, for the linear search algorithm with a bit bound of 
8, ABC achieved a $93\%$ reduction in the number of logic levels (from 529 to 33), 
and a $21\%$ reduction in the number of AND gates. For more complex designs,
such as the linked list insertion, the reduction algorithms achieved $50\%$
reduction in the number of logic levels, 
$80\%$ reduction in the number of AND gates 
and $58\%$ reduction in the number of latches. 

On average, the ABC synthesis algorithms achieved $43\%$ reduction in the 
number of latches, $53\%$ reduction in the number of AND gates and 
$47\%$ reduction in the number of logic levels. Therefore we can conclude
that \mytool{} can effectively make use of ABC's synthesis algorithm to 
reduce the problem by half and thus help the proof algorithms. Furthermore, 
we note that even in the cases where the ABC solver was not able to 
provide a conclusive result about the properties to verify, \mytool{} was
still able to generate and efficiently reduce the AIG circuits. This in fact
allows us to try the validity checks using higher time-out limits and BDD size limits, 
or  try new proof algorithms in the future.
%The reduction rate that the ABC synthesis algorithms can achieve in terms
%of the number of latches can be sometime limited by the nature of the 
%program \Pm, and the number of variables in it. Since we wrote our algorithms
%in a way to minimize unused variables in the code
%Since the number of latches in the AIG is highly dependent on the 
%number of variables in the program \Pm and the provided bit width, 
%the reduction rate that the ABC synthesis algorithms can be sometimes 
%limited 

\section{SV-COMP 2013 benchmarks}
\label{chap:res:svcompbench}
\input{svcomp}