%% svcompetition benchmarks
We evaluated \mytool{} against a select set of benchmarks obtained from the
second competition on Software Verification SVCOMP'13~\cite{svcomp}.
We selected the benchmarks from the {\em ControlFlowInteger} and the {\em Loops}
and compare the execution time obtained from running \mytool{} with the 
tools ranked first, second and third in each of the two categories. 

\input{table_svcomp}

Table~\ref{tb:svcomp} summarizes the results obtained from running \mytool{} on the
select set of SVCOMP'13 benchmarks. The first column shows the name of the 
benchmark as presented in the competition. The {\em status} column shows the decision 
that \mytool{} returned, it is colored in green to indicate that the results are accurate, \ie
\mytool{} produced no false negative nor false positives. 
We report on the total execution time taken by \mytool{}, the winner on the category ({\em gold}),
the first runner ({\em silver}) and the second runner ({\em bronze}) for each of the selected
benchmarks. Additionally, we report on the average execution time taken by each of the four 
tools for each of the two categories from which we selected the benchmarks. 
The benchmarks labeled \cci{locks\_*} belong to the {\em ControlFlowInteger} category,
while the remaining benchmarks belong to the {\em Loops} category. 

In the {\em ControlFlowInteger} category, \mytool{} outperformed the bronze tool 
on all of the benchmarks. It was also able to outperform the silver tool
on the first six safe benchmarks and outperform the golden tool on the 
first two. For the unsafe benchmarks, \mytool{} surpassed the other tools 
and was able to find a counterexample $1.7$ times faster than the fastest tool.
On average, \mytool{} topped the bronze tool and was ranked very closely behind
the silver one. 

In the {\em Loops} category, \mytool{} surpassed both of the silver and the 
bronze tools on all of the benchmarks and came very close the gold tool.
In fact, the silver tool produced a false counterexample on the \cci{count\_up\_down\_s}
benchmark and the bronze tool produced a false counterexample on the \cci{invert\_string\_s}
benchmark. \mytool{} was able to accurately verify and disprove all of the benchmarks. 
On average, \mytool{} ranked second outperforming both the silver and the bronze tools, and
came very closely behind the gold tool. 